%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Summary}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}

%---------------------------------------------------------
Mechatronics and Software Engineer at EXOM Engineering, a company in Spain developing solutions with AI, high speed processing and machine vision around the laser industry. I studied in Germany and worked since 2016 in real client projects, gaining experience in large teams in the areas of support, frontend, backend and project management. I co-founded EXOM Engineering in 2018, leading the development of software for end users and implementing large scale systems in the company to improve production and organization. 

  

DevOps Engineer at fintech \& blockchain company Dunamu which is known for operating Upbit, the largest cryptocurrency exchange in Korea. Have led growth at infrastructure departments in two fintech companies as lead engineer and founding member. 12+ years of diverse software engineering experience with specialties in software architecture design, infrastructure operation, backend development, and security engineering.

Love to contribute to open sources and tech communities by sharing knowledge and experience. Prefers a command line interface environment as a big fan of Vim, Linux, and macOS. Always trying to customize to find the most optimal environment. Interested in devising a better problem-solving method for challenging tasks, and learning new technologies and tools.
\end{cvparagraph}
